COG-ED Manuscript

### 2022-01-20 06_Paper/COG-ED/Manuscript.Rmd

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#apa_table(
#  h2c_ss.table
#  , caption = "Simple slope analysis of SVs...XXX"
#  , note = "XXX."
#  , escape = FALSE
#)
```

>>>>

```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  h2c_ss.table
  , caption = "Simple slope analysis of SVs...XXX"
  , note = "XXX."
  , escape = TRUE
)
```
